### 2024-12-04 manuscript.tex
Update on Overleaf.
Addressing comments

\subsection{ICON}

@@

Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality)
coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
has so far produced four cycles of model runs. We used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
use it due to a lack of availability of the necessary variables. The horizontal
resolution of ngc3028 is about 5 km.  The model output is available on 90
vertical levels and 3-hourly instantaneous temporal resolution.  Unlike current
general circulation models (GCMs), the storm-resolving version of ICON does not
use convective and cloud parameterization but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterizations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterized in this model.

@@

In addition to the above, we partitioned our data into two mutually exclusive
subsets based on lower tropospheric stability (LTS), which is derived as the difference between the potential temperature at 700 hPa
and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
all voyage tracks and stations (Fig.  \ref{fig:lts}), we determined a dividing
threshold of 12 K for relatively unstable (< 12 K) and relatively stable (>= 12
K) conditions.

@@

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
bright bias previously identified in models. In our results, this is
characterised by outgoing TOA SW radiation similar to or higher than in the
satellite observations, while at the same time total cloud fraction is
substantially underestimated relative to the ground-based lidar observations.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
other hand, this relationship is not present in ICON. This model generally
predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing TOA SW radiation is
approximately proportional to the deficit of the total cloud fraction. While this
might be a welcome feature and an improvement over previous models, it does
mean that the outgoing TOA SW radiation is overall underestimated instead of
being compensated by a higher cloud albedo. This can, of course, lead to
undesirable secondary effects such as overestimated solar heating of the sea
surface, among other factors responsible for SO SST biases in climate models
\citep{zhang2023,luo2023,hyder2018}.

>>>>

\subsection{ICON}
\label{sec:icon}

@@

Here, we use a free-running (i.e., the weather situation in the model does not correspond to reality)
coupled GSRM simulation made for the purpose of climate projection.  nextGEMS
has so far produced four cycles of model runs. We used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b} for a model
time period of 20 January 2020 to 22 July 2025, of which we analysed the period 2021--2024 (inclusive). While a Cycle 4 run was available, we could not
use it due to a lack of availability of the necessary variables. The horizontal
resolution of ngc3028 is about 5 km.  The model output is available on 90
vertical levels and 3-hourly instantaneous temporal resolution.

Unlike current general circulation models (GCMs), the storm-resolving version
of ICON does not use convective and cloud parameterization but relies on
explicit simulation of convection and clouds on the model grid. While this
makes the code development simpler without having to rely on uncertain
parameterizations, it can miss smaller-scale clouds below the grid resolution.
Turbulence and cloud microphysics are still parameterized in this model. To
account for the radiative effects of subgrid-scale clouds, a cloud
inhomogeneity factor is introduced in the model which scales down the cloud
liquid water for radiative calculations. It ranges from 0.4 at lower
tropospheric stability (LTS) of 0 K to 0.8 at 30 K. In addition, vertical
mixing is enhanced in unstable and humid lower-tropospheric conditions, which
reduces the amount of shallow clouds.

@@

In addition to the above, we partitioned our data into two mutually exclusive
subsets based on LTS, which is derived as the difference between the potential temperature at 700 hPa
and the surface.  Based on a histogram of LTS in ERA5 and MERRA-2 calculated at
all voyage tracks and stations (Fig.  \ref{fig:lts}), we determined a dividing
threshold of 12 K for relatively unstable (< 12 K) and relatively stable (>= 12
K) conditions.

@@

The relationship between cloud biases and radiation has a number of notable
features. Perhaps unsurprisingly, the reanalyses exhibit the too few, too
bright bias previously identified in models. In our results, this is
characterised by outgoing TOA SW radiation similar to or higher than in the
satellite observations, while at the same time total cloud fraction is
substantially underestimated relative to the ground-based lidar observations.
This feature seems to be much more pronounced in ERA5 than in MERRA-2. On the
other hand, this relationship is not present in ICON. This model generally
predicts smaller outgoing TOA SW radiation and smaller total cloud fraction
than observations, and the deficit of outgoing TOA SW radiation is
approximately proportional to the deficit of the total cloud fraction. While
this might be a welcome feature and an improvement over previous models, it
does mean that the outgoing TOA SW radiation is overall underestimated instead
of being compensated by a higher cloud albedo.  This can, of course, lead to
undesirable secondary effects such as overestimated solar heating of the sea
surface, among other factors responsible for SO SST biases in climate models
\citep{zhang2023,luo2023,hyder2018}.  To some extent, the cloud albedo might be
reduced in the model artifically by the application of an inhomogeneity factor
to lower cloud liquid water in the radiative transfer calculations (Sec.
\ref{sec:icon}).
